```{r load packages}
library(dplyr)
library(ggplot2)
library(tidyverse)
```

```{r dplyr:::filter}
dplyr:::filter
useBytes = TRUE
```

```{r read in file}
completeX <- read.csv("Complete DataX.csv", stringsAsFactors = FALSE, header = TRUE, sep = ",")
```

```{r getting the number of papers per species}
parmeniacapapers <- filter(completeX, grepl('Prunus armeniaca', Species))
paviumpapers <- filter(completeX, grepl('Prunus avium', Species))
pbrigantinapapers <- filter(completeX, grepl('Prunus brigantina', Species))
pcerasiferapapers <- filter(completeX, grepl('Prunus cerasifera', Species))
pcerasuspapers <- filter(completeX, grepl('Prunus cerasus', Species))
pcocomiliapapers <- filter(completeX, grepl('Prunus cocomilia', Species))
pmahalebpapers <- filter(completeX, grepl('Prunus mahaleb', Species))
pmicrocarpapapers <- filter(completeX, grepl('Prunus microcarpa', Species))
ppaduspapers <- filter(completeX, grepl('Prunus padus', Species))
pspinosapapers <- filter(completeX, grepl('Prunus spinosa', Species))
pamygdaliformispapers <- filter(completeX, grepl('Pyrus amygdaliformis', Species))
paustriacapapers <- filter(completeX, grepl('Pyrus austriaca', Species))
pcommunispapers <- filter(completeX, grepl('Pyrus communis', Species))
pcordatapapers <- filter(completeX, grepl('Pyrus cordata', Species))
pelaeagnifoliapapers <- filter(completeX, grepl('Pyrus elaeagnifolia', Species))
pnivalispapers <- filter(completeX, grepl('Pyrus nivalis', Species))
ppyrasterpapers <- filter(completeX, grepl('Pyrus pyraster', Species))
psosnovskyipapers <- filter(completeX, grepl('Pyrus sosnovskyi', Species))
ckyrtostylapapers <- filter(completeX, grepl('Crataegus X kyrtostyla', Species))
cmacrocarpapapers <- filter(completeX, grepl('Crataegus macrocarpa | Crataegus X marcrocarpa', Species))
cmediapapers <- filter(completeX, grepl('Crataegus media | Crataegus X media', Species))
ccoccineaepapers <- filter(completeX, grepl('Crataegus coccineae', Species))
claevigatapapers <- filter(completeX, grepl('Crataegus laevigata', Species))
cmonogynapapers <- filter(completeX, grepl('Crataegus monogyna', Species))
crhipidophyllapapers <- filter(completeX, grepl('Crataegus rhipidophylla', Species))
coblongapapers <- filter(completeX, grepl('Crataegus oblonga', Species))
marnoldianapapers <- filter(completeX, grepl('Malus arnoldiana | Malus X arnoldiana', Species))
mrobustapapers <- filter(completeX, grepl('Malus robusta | Malus X robusta', Species))
mspectabilispapers <- filter(completeX, grepl('Malus spectabilis | Malus X spectabilis', Species))
mbaccatapapers <- filter(completeX, grepl('Malus baccata', Species))
mdomesticapapers <- filter(completeX, grepl('Malus domestica | Malus X domestica', Species))
morientalispapers <- filter(completeX, grepl('Malus orientalis', Species))
mpumilapapers <- filter(completeX, grepl('Malus pumila', Species))
msieversiipapers <- filter(completeX, grepl('Malus sieversii', Species))
msylvestrispapers <- filter(completeX, grepl('Malus sylvestris', Species))
mtrilobatapapers <- filter(completeX, grepl('Malus trilobata', Species))
mfloribundapapers <- filter(completeX, grepl('Malus floribunda | Malus X floribunda', Species))
sslovenicapapers <- filter(completeX, grepl('Sorbus slovenica | Sorbus X slovenica', Species))
sariapapers <- filter(completeX, grepl('Sorbus aria', Species))
saustriacapapers <- filter(completeX, grepl('Sorbus austriaca', Species))
schamaemespiluspapers <- filter(completeX, grepl('Sorbus chamaemespilus', Species))
sdomesticapapers <- filter(completeX, grepl('Sorbus domestica | Sorbus X domestica', Species))
sintermediapapers <- filter(completeX, grepl('Sorbus intermedia', Species))
slatifoliapapers <- filter(completeX, grepl('Sorbus latifolia', Species))
smougeotiipapers <- filter(completeX, grepl('Sorbus mougeotii', Species))
storminalispapers <- filter(completeX, grepl('Sorbus torminalis', Species))
###below not from original list but were included
malinaepapers <- filter(completeX, grepl('Malinae', Species))
napapers <- filter(completeX, grepl('NA', Species))
pdomesticapapers <- filter(completeX, grepl('Prunus domestica', Species))
pyspinosapapers <- filter(completeX, grepl('Pyrus spinosa', Species))
saucupariapapers <- filter(completeX, grepl('Sorbus aucuparia', Species))
scordigastensispapers <- filter(completeX, grepl('Sorbus cordigastensis', Species))
slegreipapers <- filter(completeX, grepl('Sorbus legrei | Sorbus leigrei', Species))
smilensispapers <- filter(completeX, grepl('Sorbus milensis', Species))
squerneapapers <- filter(completeX, grepl('Sorbus quernea', Species))
sremensispapers <- filter(completeX, grepl('Sorbus remensis', Species))
sorbuspapers <- filter(completeX, grepl('Sorbus sp | Sorbus spp', Species))
```

```{r DO IT ALL OVER AGAIN THANKS TO MARTIN!}
df <- completeX %>% group_by(Species) %>% count(Title) %>% count() %>% view()
write.csv(df, file = "speciespapers.csv")
df2 <- completeX %>% group_by(Study.Locale) %>% count(Title) %>% count() %>% view()
write.csv(df2, file = "localepapers.csv")
df3 <- completeX %>% group_by(Conservation.Recommendation) %>% count(Title) %>% count() %>% view()
write.csv(df3, "conrecpapers.csv")
df4 <- completeX %>% group_by(Number.of.Sites) %>% count(Title) %>% count() %>% view()
write.csv(df4, file = "numsitepapers.csv")
df5 <- completeX %>% group_by(Accessions) %>% count(Title) %>% count() %>% view()
write.csv(df5, file = "accessionpapers.csv")
df6 <- completeX %>% group_by(Individuals) %>% count(Title) %>% count() %>% view()
write.csv(df6, file = "indivipapers.csv")
df7 <- completeX %>% group_by(Cultivars) %>% count(Title) %>% count() %>% view()
write.csv(df7, file = "cultpapers.csv")
df8 <- completeX %>% group_by(Keyword) %>% count(Title) %>% count() %>% view()
write.csv(df8, file = "keywordpapers.csv")
df9 <- completeX %>% group_by(Threat) %>% count(Title) %>% count() %>% view()
write.csv(df9, file = "threatpapers.csv")
df10 <- completeX %>% group_by(Impact.of.Threat) %>% count(Title) %>% count() %>% view()
write.csv(df10, file = "impactthreatpapers.csv")
df11 <- completeX %>% group_by(Management.Recommendation) %>% count(Title) %>% count() %>% view()
write.csv(df11, file = "mngmtrecpapers.csv")
df12 <- completeX %>% group_by(Impact.of.Conservation.Recommendation) %>% count(Title) %>% count() %>% view()
write.csv(df12, file = "impactconrec.csv")
df13 <- completeX %>% group_by(Genetic.Topic) %>% count(Title) %>% count() %>% view()
write.csv(df13, file = "gentoppapers.csv")
df14 <- completeX %>% group_by(Population.Type) %>% count(Title) %>% count() %>% view()
write.csv(df14, file = "poptypepapers.csv")
df15 <- completeX %>% group_by(Data.Type) %>% count(Title) %>% count() %>% view()
write.csv(df15, file = "datatypepapers.csv")
df16 <- completeX %>% group_by(Habitat) %>% count(Title) %>% count() %>% view()
write.csv(df16, file = "habitatpapers.csv")
##this essentially joins and then unjoins the columns so that the proper count can be conducted by dplyr
```

```{r save files}
save(completeX, file = "completeX.RData")
```

```{r cleaner data}
cleanerdataX <- read.csv("Cleaner DataX.csv", header = TRUE, stringsAsFactors = FALSE)
```

```{r create figure of papers per species}
library(ggplot2)
ggplot(cleanerdataX, aes(n, Species))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Papers per Species", x="Number of Papers", y="Species", y = guide_axis(n.dodge = -2))+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,75))+
  theme(axis.text.y.left = element_text (size = 5))
```

```{r number of papers per location}
library(ggplot2)
ggplot(cleanerdataX, aes(n2, Study.Locale))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Papers per Locale", x="Number of Papers", y="Locale")+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,50))+
  theme(axis.text.y.left = element_text (size = 5))
```

```{r number of papers per genetic topic}
library(ggplot2)
ggplot(cleanerdataX, aes(n13, Genetic.Topic))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Papers per Genetic Topic", x="Number of Papers", y="Genetic Topic")+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,120))+
  theme(axis.text.y.left = element_text (size = 5))
```

```{r papers per keyword}
library(ggplot2)
ggplot(cleanerdataX, aes(n7, Keyword))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Papers per Keyword", x="Number of Papers", y="Keyword")+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,45))+
  theme(axis.text.y.left = element_text (size = 3))
```

```{r Okay let's make some consensus graphs}
categoriesdata <- read.csv("CategoriesData.csv", header = TRUE, stringsAsFactors = FALSE)
```

```{r plots of categories}
library(ggplot2)
ggplot(categoriesdata, aes(n, Threats))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Threats", x="Number of Papers", y="Threats")+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,100))+
  theme(axis.text.y.left = element_text (size = 8))
ggplot(categoriesdata, aes(n2, Threat.Impacts))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Threat Impacts", x="Number of Papers", y="Threat Impacts")+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,60))+
  theme(axis.text.y.left = element_text (size = 8))
ggplot(categoriesdata, aes(n3, Management.Recommendations))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Management Recommendations", x="Number of Papers", y="Management Recommendations")+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,140))+
  theme(axis.text.y.left = element_text (size = 8))
ggplot(categoriesdata, aes(n4, Conservation.Recommendations))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Conservation Recommendations", x="Number of Papers", y="Conservation Recommendations")+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,45))+
  theme(axis.text.y.left = element_text (size = 8))
ggplot(categoriesdata, aes(n5, Conservation.Recommendation.Impacts))+
  geom_bar(stat = "identity")+
  theme_bw()+
  labs(title = "Conservation Recommendation Impacts", x="Number of Papers", y="Conservation Recommendation Impacts")+
  scale_x_continuous(expand = c(0,0))+
  coord_cartesian(xlim = c(0,70))+
  theme(axis.text.y.left = element_text (size = 8))
```

```{r getting the correct counts}
dfXXX <- completeX %>% group_by(Species) %>% count(Study.Locale) %>% count() %>% view()
write.csv(dfXXX, file = "speciesincountries.csv")
```

```{r getting the correct counts}
dfc <- completeX %>% group_by(Study.Locale) %>% count(Species) %>% count() %>% view()
write.csv(dfc, file = "countrybyspp.csv")
```

```{r read in categorized papers}
catpapers <- read.csv("CategorizedPapers.csv", header = TRUE,
                      stringsAsFactors = FALSE)
```

```{r sd of papers per species}
data(catpapers)
na.omit(catpapers)
ln <- catpapers$Species
cat("The standard deviation of Species is: ", "\n")
sd(ln, na.rm = FALSE)
```

```{r M Braun code}
library(tidyverse)
path <- "C:/Users/martin.braun/Documents/Projekte/Support/Lila/"
cat <- clean$Study.Locale[!is.na(clean$Study.Locale)]
reps <- clean$n2[!is.na(clean$n2)]
locale <- rep(cat, reps)
chisq.test(table(locale))
# Be aware that given probabilities are assumed to be rep(1/length(x))
# Basically you test if an outcome is different from expected probabilities
```

```{r Attempt Chi Sq Test}
cats <- read.csv("CategoriesData.csv", header = TRUE,
                 stringsAsFactors = FALSE)
cat <- cats$Threats[!is.na(cats$Threats)]
cat <- cat[1:6]
reps <- cats$n[!is.na(cats$n)]
threats <- rep(cat, reps)
chisq.test(table(threats))
```

```{r Chi Sq Test}
cat <- categoriesdata$Threats[!is.na(categoriesdata$Threats)]
cat <- cat[1:5]
reps <- categoriesdata$n[!is.na(categoriesdata$n)]
threats <- rep(cat, reps)
chisq.test(table(threats))
```

```{r load package and file}
contingency <- read.csv("Contingency Table of Categories to Species.csv"
                        , header = TRUE, stringsAsFactors = FALSE)
#install.packages('rcompanion')
#library(rcompanion)
```

```{r try Cramer's V}
#create matrix
data <- matrix(c(3, 10, 1, 0, 0, 0, 35, 5, 1, 62, 0, 1, 1, 0, 10, 0, 4, 2, 5, 0, 0, 8, 1, 0, 1, 3, 0, 0, 1, 21, 0, 0, 0, 2, 0, 0, 0, 47, 3, 6, 1, 0, 0, 0, 30, 5, 1, 59, 0, 1, 0, 0, 8, 0, 2, 2, 5, 0, 0, 7, 1, 0, 1, 3, 0, 0, 1, 16, 0, 0, 0, 1, 0, 0, 0, 39, 1, 18, 1, 2, 0, 0, 40, 7, 1, 99, 1, 4, 1, 4, 15, 2, 7, 12, 8, 0, 0, 9, 1, 0, 6, 6, 0, 0, 1, 30, 0, 1, 1, 0, 0, 1, 1, 70, 1, 11, 0, 0, 0, 0, 27, 2, 0, 43, 0, 0, 0, 0, 2, 1, 3, 4, 1, 0, 0, 4, 0, 0, 5, 3, 0, 0, 1, 19, 0, 1, 0, 3, 0, 0, 0, 42, 1, 9, 0, 0, 0, 0, 21, 2, 0, 32, 0, 1, 0, 0, 6, 1, 2, 4, 1, 0, 0, 4, 0, 0, 2, 3, 0, 0, 1, 19, 0, 1, 1, 0, 0, 1, 1, 42))
mat1 <- matrix(data, ncol = 5)
mat2 <- mat1[rowSums(mat1) != 0, ]

#Cramer's V
cramerV(mat2)
```

```{r Contingency Means, SD, and SE}
contingency <- read.csv("Contingency Table of Categories to Species.csv"
                        , header = TRUE, stringsAsFactors = FALSE)
mean(contingency$Threats)
mean(contingency$Threat.Impacts)
mean(contingency$Management.Recommendations)
mean(contingency$Conservation.Recommendations)
mean(contingency$Conservation.Recommendation.Impacts)
sd(contingency$Threats)
sd(contingency$Threat.Impacts)
sd(contingency$Management.Recommendations)
sd(contingency$Conservation.Recommendations)
sd(contingency$Conservation.Recommendation.Impacts)
13.37263/(sqrt(224)) #threats
11.9701/(sqrt(192)) #threat impacts
10.42983/(sqrt(177)) #conservation recommendations
9.087147/(sqrt(158)) #conservation recommendation impacts
19.89297/(sqrt(358)) #management recommendations
```

```{r Subcats Means, SD, and SE}
subcats <- read.csv("Contingency Table of Categories to Subcats.csv",
                    header = TRUE, stringsAsFactors = FALSE)
mean(subcats$Threats)
mean(subcats$Threat.Impacts)
mean(subcats$Conservation.Recs)
mean(subcats$Conservation.Rec.Impacts)
mean(subcats$Management.Recs)
sd(subcats$Threats)
sd(subcats$Threat.Impacts)
sd(subcats$Conservation.Recs)
sd(subcats$Conservation.Rec.Impacts)
sd(subcats$Management.Recs)
22.36419/(sqrt(177)) #threats
14.49253/(sqrt(154)) #threat impacts
13.9342/(sqrt(172)) #conservation recommendations
15.92766/(sqrt(142)) #conservation recommendation impacts
34.77259/(sqrt(350)) #management impacts
```

```{r Mean and SE of Subcats}
categoriesdata <- read.csv("CategoriesData.csv", header = TRUE, 
                           stringsAsFactors = FALSE)
realcategoriesdata <- read.csv("CategoriesDataReal.csv", header = TRUE,
                               stringsAsFactors = FALSE)
##CategoriesData has the number of papers per category and total number of papers
meansandse <- read.csv("Means and SE.csv", header = TRUE, 
                       stringsAsFactors = FALSE)
##Means and SE has the total papers associated per variable, percentage of papers per category within variable, and the M and SE of each variable, each SE was calculated by calculating first the SD was calculated in R and then the SE was manually calculated also using R

##get rid of NAs
na.omit(categoriesdata)

##the below calculations are means for each variable
177/5 #threats
154/7 #threat impacts
350/9 #mngmt recs
172/7 #con recs
142/6 #con rec impacts

##create objects of the SD for each variable
threats <- sd(categoriesdata$n)
threatimps <- sd(categoriesdata$n2)
mngmtrecs <- sd(categoriesdata$n3)
conrecs <- sd(categoriesdata$n4) 
conrecimps <- sd(categoriesdata$n5)

##the below calculates the SE based on the established euation (SE = SD/sqrt(n))
threats/(sqrt(177))
threatimps/(sqrt(154))
mngmtrecs/(sqrt(350))
conrecs/(sqrt(172))
conrecimps/(sqrt(142))
```

```{r SD and SE of Categories Data}
catsdata <- read.csv("Means and SE.csv", header = TRUE, 
                     stringsAsFactors = FALSE)
threats <- sd(catsdata$Threats)
threatimps <- sd(catsdata$Threat.Impacts)
mngmtrecs <- sd(catsdata$Management.Recs)
conrecs <- sd(catsdata$Conservation.Recs) 
conrecimps <- sd(catsdata$Conservation.Rec.Impacts)
threats/(sqrt(177))
threatimps/(sqrt(154))
mngmtrecs/(sqrt(350))
conrecs/(sqrt(172))
conrecimps/(sqrt(142))
```

```{r redo means, SE, SD}
#calculations: 
#M = total number of papers per variable/number of categories per variable
#SD = sd(data$variable)
#SE = SD/sqrt(number of papers per variable)

#read in data files
threat <- read.csv("threat.csv", header = TRUE, stringsAsFactors = FALSE)
threatimps <- read.csv("threatimpacts.csv", header = TRUE, 
                       stringsAsFactors = FALSE)
conrecs <- read.csv("conrecommendations.csv", header = TRUE,
                    stringsAsFactors = FALSE)
conrecimps <- read.csv("conrecimpacts.csv", header = TRUE,
                       stringsAsFactors = FALSE)
mngmt <- read.csv("mngmtrecommendations.csv", header = TRUE,
                  stringsAsFactors = FALSE)
#M
177/5 #threats
154/7 #threat impacts
350/9 #management recommendations
172/7 #conservation recommendations
142/6 #conservation recommendation impacts

#SD
t <- sd(threat$n)
timps <- sd(threatimps$n2)
conrec <- sd(conrecs$n3)
cimps <- sd(conrecimps$n4)
mngmtrec <- sd(mngmt$n5)

#SE
t/(sqrt(177))
timps/(sqrt(154))
conrec/(sqrt(172))
cimps/(sqrt(142))
mngmtrec/(sqrt(350))

##manual calculation of SD
#threats cat 1 (15-35.4)^2; cat 2 (94-35.4)^2; cat 3 (47-35.4)^2; cat 4 (12-35.4)^2; cat 5 (9-35.4)^2
sdthreat <- sqrt((((15-35.4)^2)+((94-35.4)^2)+((47-35.4)^2)+((12-35.4)^2)+
               ((9-35.4)^2))/5)

##calculate SE
sdthreat/(sqrt(177))
```

```{r make bar chart of total variables per genus}
totals <- read.csv("totalvariablespergenus.csv", header = TRUE,
                   stringsAsFactors = FALSE)
library(ggplot2)
library(viridis)

total <- ggplot(totals, aes(fill = Variable, x = Value, y = Genus))+
  geom_bar(position = "dodge", stat = "identity")+
  scale_fill_viridis(discrete = TRUE)+
  #ggtitle("Total Number of Variables per Taxon")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8))+
  labs(y = "Taxon", x = "n", size = 10)
plot(total)
#ggsave("totalnumbervariablespergenus.png", total, width = 11, height = 8.5)
```

```{r read in files}
byspecies <- read.csv("StackedBarSpp.csv", header = TRUE, 
                      stringsAsFactors = FALSE)
categorized <- read.csv("CategorizedPapers.csv", header = TRUE,
                        stringsAsFactors = FALSE)
require(tidyverse)
require('reshape2')

data_melt<-melt(categorized, id=c('Authors', 'Paper.Title', 'Year.Published', 'Genus', 'Species'))
unique(data_melt$variable)
unique(data_melt$value)


data_melt$variable<-as.character(data_melt$variable)
a<-data_melt %>% ungroup()%>% dplyr::group_by('Genus', 'Species','variable') %>% summarise(n=n())




```

```{r load libraries}
library(tidyverse)
library(viridisLite)
library(ggplot2)
```

```{r create a circular stacked bar plot}
data <- data.frame(
  individual = paste("Crataegus Laevigata", "Crataegus monogyna", 
                     "Cydonia oblonga", "Malinae", "Malus orientalus",
                     "Malus sieversii", "Malus sylvestris", 
                     "Malus X domestica", "Prunus armeniaca",
                     "Prunus avium", "Prunus brigantina", 
                     "Prunus cerasifera", "Prunus cerasus",
                     "Prunus cocomilia", "Prunus domestica",
                     "Prunus mahaleb", "Prunus microcarpa", 
                     "Prunus padus", "Prunus spinosa", "Pyrus communis", 
                     "Pyrus eleagnifolia", "Pyrus nivalis",
                     "Pyrus pyraster", "Pyrus spinosa", "Sorbus",
                     "Sorbus aria", "Sorbus aucuparia",
                     "Sorbus austriaca", "Sorbus chamaemespilus",
                     "Sorbus cordigastensis", "Sorbus domestica",
                     "Sorbus intermedia", "Sorbus latifolia",
                     "Sorbus legrei", "Sorbus milensis",
                     "sorbus mougeotii", "Sorbus quernea", 
                     "Sorbus remensis", "Sorbus torminalis", sep = ""),
  group = c(rep('Crataegus', 2), rep('Cydonia', 1), rep('Malus', 5),
            rep('Prunus', 11), rep('Pyrus', 5), rep('Sorbus', 15)),
  Passive = c(1,2,0,0,0,0,5,0,0,6,0,0,0,0,0,1,0,3,2,0,0,0,0,0,0,5,2,
              0,0,0,3,0,1,0,0,0,0,0,3),
  Connectivity = c(0,2,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                   0,0,0,0,0,3,0,0,0,0,0,0,0,7),
  In.Situ = c(0,2,0,0,0,0,7,1,0,14,0,0,0,0,0,1,0,0,2,0,0,0,1,0,0,0,
              1,0,0,1,3,0,0,0,2,0,0,0,10),
  Ex.Situ = c(0,0,0,0,0,0,7,1,0,8,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,
              0,0,0,4,0,0,0,0,0,0,0,10),
  Genetic = c(0,3,0,0,0,0,5,0,0,9,0,0,0,0,0,0,1,0,0,1,0,0,2,0,0,0,0,
              0,0,0,1,0,0,0,0,0,0,0,5),
  Other = c(0,1,0,0,0,0,1,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,
            0,0,0,0,0,0,1,0,0,0,1),
  Reproduction = c(0,1,0,0,0,0,1,0,0,5,0,0,0,0,0,0,0,0,0,0,0,0,0,0,
                   0,0,0,0,0,0,5,0,0,0,0,0,0,0,6)
)

# Transform data in a tidy format (long format)
data <- data %>% gather(key = "observation", value="value", -c(1,2)) 
 
# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(data$group)*nObsType, ncol(data)) )
colnames(to_add) <- colnames(data)
to_add$group <- rep(levels(data$group), each=empty_bar*nObsType )
data <- rbind(data, to_add)
data <- data %>% arrange(group, individual)
data$id <- rep( seq(1, nrow(data)/nObsType) , each=nObsType)
 
# Get the name and the y position of each label
label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)
 
# prepare a data frame for base lines
base_data <- data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))
 
# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]
 
# Make the plot
p <- ggplot(data) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
  scale_fill_viridis(discrete=TRUE) +
  
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +
  
  ylim(-150,max(label_data$tot, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +
  
  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=tot+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +
  
  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)


# Save at png
ggsave(p, file="output.png", width=10, height=10)

# Received error: Error in `check_aesthetics()`:
#! Aesthetics must be either length 1 or the same as the data (6): hjust
```

```{r Circular Stacked Bar Chart Reference Code}
# library
library(tidyverse)
library(viridisLite)
 
# Create dataset
data <- data.frame(
  individual=paste( "Mister ", seq(1,60), sep=""),
  group=c( rep('A', 10), rep('B', 30), rep('C', 14), rep('D', 6)) ,
  value1=sample( seq(10,100), 60, replace=T),
  value2=sample( seq(10,100), 60, replace=T),
  value3=sample( seq(10,100), 60, replace=T)
)
 
# Transform data in a tidy format (long format)
data <- data %>% gather(key = "observation", value="value", -c(1,2)) 
 
# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(data$group)*nObsType, ncol(data)) )
colnames(to_add) <- colnames(data)
to_add$group <- rep(levels(data$group), each=empty_bar*nObsType )
data <- rbind(data, to_add)
data <- data %>% arrange(group, individual)
data$id <- rep( seq(1, nrow(data)/nObsType) , each=nObsType)
 
# Get the name and the y position of each label
label_data <- data %>% group_by(id, individual) %>% summarize(tot=sum(value))
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)
 
# prepare a data frame for base lines
base_data <- data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))
 
# prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]
 
# Make the plot
p <- ggplot(data) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
  #scale_fill_viridis(discrete=TRUE) +
  
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  
  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6 , angle=0, fontface="bold", hjust=1) +
  
  ylim(-150,max(label_data$tot, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +
  
  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=tot+10, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=5, angle= label_data$angle, inherit.aes = FALSE ) +
  
  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)


# Save at png
ggsave(p, file="output.png", width=10, height=10)
```

```{r stacked bar charts}
#simple stacked reference code
# library
library(ggplot2)
 
# create a dataset
specie <- c(rep("sorgho" , 3) , rep("poacee" , 3) , rep("banana" , 3) , rep("triticum" , 3) )
condition <- rep(c("normal" , "stress" , "Nitrogen") , 4)
value <- abs(rnorm(12 , 0 , 15))
data <- data.frame(specie,condition,value)
 
# Stacked
ggplot(data, aes(fill=condition, y=value, x=specie)) + 
    geom_bar(position="stack", stat="identity")

#percent stacked reference code
 # library
library(ggplot2)
 
# create a dataset
specie <- c(rep("sorgho" , 3) , rep("poacee" , 3) , rep("banana" , 3) , rep("triticum" , 3) )
condition <- rep(c("normal" , "stress" , "Nitrogen") , 4)
value <- abs(rnorm(12 , 0 , 15))
data <- data.frame(specie,condition,value)
 
# Stacked + percent
ggplot(data, aes(fill=condition, y=value, x=specie)) + 
    geom_bar(position="fill", stat="identity")
```

```{r multiple box plots in one chart + read in files}
#data to load
species <- read.csv("Contingency Table of Categories to Species.csv", 
                    header = TRUE, stringsAsFactors = FALSE)
subcat <- read.csv("Contingency Table of Categories to Subcats.csv",
                   header = TRUE, stringsAsFactors = FALSE)

#create box plot that displays paper distribution for each spp base R
boxplot(Threats~Species,
data = species,
main = "Paper Distribution Per Species",
xlab ="Species",
ylab ="Threats",
col ="steelblue",
border ="black")
#ugly honestly

#create box plot with ggplot
library(ggplot2)
ggplot(data = subcat, aes(x = Threats, y = X)) +
  geom_boxplot(fill = "grey") +
  labs(x = "Threats", y = "Subcategory")
#seems really iffy

ggplot(data = species, aes(x = Threats, y = Species)) +
  geom_boxplot(fill = "grey") +
  labs(x = "Threats", y = "Species")
#this has gotta be fake honestly
```

```{r M, SD, SE for subcats and species FINAL}
#calculations: 
#M = total number of papers per variable/number of categories per variable
#SD = sd(data$variable)
#SE = SD/sqrt(number of papers per variable)

#M Subcats
177/5 #threats
154/7 #threat impacts
350/9 #management recommendations
172/7 #conservation recommendations
142/6 #conservation recommendation impacts

#M Species
224/21 #threats
192/20 #threat impacts
358/30 #management recommendations
177/19 #conservation recommendations
158/22 #conservation recommendation impacts

#SD Subcats
sd(subcat$Threats)
sd(subcat$Threat.Impacts)
sd(subcat$Management.Recs)
sd(subcat$Conservation.Recs)
sd(subcat$Conservation.Rec.Impacts)

#SD Species
sd(species$Threats)
sd(species$Threat.Impacts)
sd(species$Management.Recommendations)
sd(species$Conservation.Recommendations)
sd(species$Conservation.Recommendation.Impacts)

#SE Subcats
22.36419/(sqrt(177)) #threats
14.49253/(sqrt(154)) #threat impacts
34.77259/(sqrt(350)) #management recommendations
13.9342/(sqrt(172)) #conservation recommendations
15.92766/(sqrt(142)) #conservation recommendation impacts

#SE Species
13.23128/(sqrt(224)) #threats
11.84126/(sqrt(192)) #threat impacts
19.68593/(sqrt(358)) #management recommendations
10.32023/(sqrt(177)) #conservation recommendations
8.992732/(sqrt(158)) #conservation recommendation impacts
```

```{r Cramer's V Test Subcats and Species}
#install.packages("rcompanion")
library(rcompanion)
#create matrix of species per category
data <- matrix(c(3, 10, 1, 0, 0, 0, 35, 5, 1, 62, 0, 1, 0, 1, 0, 10, 0, 4, 2, 5, 0, 0, 8, 1, 0, 0, 1, 3, 0, 0, 1, 21, 0, 0, 0, 2, 0, 0, 0, 47, 3, 6, 1, 0, 0, 0, 30, 5, 1, 59, 0, 1, 0, 0, 0, 8, 0, 2, 2, 5, 0, 0, 7, 1, 0, 0, 1, 3, 0, 0, 1, 16, 0, 0, 0, 1, 0, 0, 0, 39, 1, 18, 1, 2, 0, 0, 40, 7, 1, 99, 1, 1, 3, 1, 4, 15, 2, 7, 12, 8, 0, 0, 9, 1, 8, 0, 6, 6, 0, 0, 1, 30, 0, 1, 1, 0, 0, 1, 1, 70, 1, 11, 0, 0, 0, 0, 27, 2, 0, 43, 0, 0, 0, 0, 0, 2, 1, 3, 4, 1, 0, 0, 4, 0, 4, 0, 5, 3, 0, 0, 1, 19, 0, 1, 0, 3, 0, 0, 0, 42, 1, 9, 0, 0, 0, 0, 21, 2, 0, 32, 0, 0, 1, 0, 0, 6, 1, 2, 4, 1, 0, 0, 4, 0, 3, 0, 2, 3, 0, 0, 1, 19, 0, 1, 1, 0, 0, 1, 1, 42))
mat1 <- matrix(data, ncol = 5)
mat2 <- mat1[rowSums(mat1) != 0, ]

#Cramer's V
cramerV(mat2)

#create matrix of subcategory per category
data2 <- matrix(c(0, 0, 0, 0, 94, 0, 0, 47, 0, 0, 9, 0, 0, 12, 0, 0, 15, 0, 0, 0, 0, 0, 0, 0, 2, 18, 0, 0, 59, 0, 0, 12, 0, 18, 0, 27, 0, 0, 0, 0, 0, 18, 0, 0, 13, 0, 0, 30, 0, 27, 43, 0, 5, 36, 0, 0, 0, 0, 18, 0, 0, 0, 0, 10, 0, 0, 0, 0, 0, 0, 69, 0, 0, 17, 0, 0, 0, 0, 26, 0, 0, 8, 12, 0, 0, 14, 0, 0, 0, 16, 138, 43, 0, 60, 1, 71, 2, 0, 0, 0, 0, 5, 0, 0, 0))
mat3 <- matrix(data2, ncol = 5)
mat4 <- mat3[rowSums(mat3) != 0, ]

#Cramer's V
cramerV(mat4)
```

```{r genetic groupings plot}
#Libraries
library(ggplot2)
library(dplyr)
library(viridis)

#The dataset is provided in the gapminder library
#library(gapminder)
#data <- gapminder %>% filter(year=="2007") %>% dplyr::select(-year)

#read in data
gentops <- read.csv("Appendix_Genetic_topics.csv", header = TRUE,
                    stringsAsFactors = FALSE)

#make bubble plot
#ggplot(gentops, aes(x = Genetic.Topic, y = Number.of.Papers.1)) +
 # geom_histogram()

